---
title: "p8105_hw5_sl5232"
author: "Shangsi Lin"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Load in data on homicides in large U.S. cities.

```{r}
homicides_df = read.csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"))
```

Observing the data set, which has `r nrow(homicides_df)` rows of observations and `r ncol(homicides_df)` columns of variables. We see that raw data is about homicides information across U.S. There are variables such as the id of the homicides, the date of report, victim's information, location that homicides belong to, and the disposition status.

Next, create a `city_state` variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides(for which the disposition is "Closed without arrest" or "Open/No arrest").

```{r}
homicides_df =
  homicides_df %>%
  mutate(city_state = str_c(city, state, sep = ",")) %>% 
  group_by(city_state) 

tibble_total = summarise(homicides_df, total_homicides = n())

tibble_unsolved =
  homicides_df %>% 
  filter(disposition != "Closed by arrest") %>% 
  summarise(unsolved_homicides = n()) 

homicides_condition = full_join(tibble_total, tibble_unsolved) %>% 
  replace(is.na(.), 0)

homicides_condition
```

Estimate the proportion of homicides that are unsolved for the city of Baltimore, MD. Save it as an R object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_result = 
  filter(homicides_condition, city_state == "Baltimore,MD")

baltimore_test =
  prop.test(x = baltimore_result$unsolved_homicides,n = baltimore_result$total_homicides) %>% 
  broom::tidy()

baltimore_test
```

Next, run the similar test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. 

```{r}
total_test = homicides_condition %>%
  mutate(prop_test = map2(.x = unsolved_homicides , .y = total_homicides , ~prop.test(x = .x,n = .y))) %>%
  mutate(prop_test = map(prop_test,broom::tidy)) %>%
  unnest(prop_test) %>%
  select(city_state, estimate, starts_with("conf."))
total_test
```

Create a plot that shows the estimates and CIs for each city with error bars based on upper and lower limites. The cities are organized according to the proportion of unsolved homicides.

```{r}
total_test %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  labs(
    x = "City,State",
    y = "Percentage of unsolved homicides",
    title = "Percentage of unsolved homicides across U.S."
  )  +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) 
```

## Problem 3

For n = 30, sigma = 5, set mu = 0 and generate 5000 datasets from the model of a normal distribution, and save mu-hat and the p-value arising from the test of H: mu = 0 using alpha = 0.05. 

```{r sim1}
simulation = function(size = 30, mu = 0, sigma = 5) {
  x = rnorm(n = size, mean = mu, sd = sigma)
  t.test(x, n = size, conf.level = 0.95)
}

sim_0 = vector("list", length = 100)

for (i in 1:5000) {
  sim_0[[i]] = simulation() %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}

bind_rows(sim_0)
```

Then repeat for mu = {1,2,3,4,5,6}, also combine it with the situation where mu = 0. 

```{r sim2}
sim_all = expand_grid(
  sample_size = 30,
  real_mu = 0:6,
  iteration = 1:5000
) %>% 
  mutate(temp_df = map2(.x = sample_size, .y = real_mu, ~broom::tidy(simulation(size = .x, mu = .y)))) %>% 
  unnest(temp_df) %>% 
  select(real_mu, estimate, p.value)
```

Next, make a plot showing the proportion of times the null was rejected on the y axis and the true value of mu on the x axis.

```{r}
sim_summary =
  sim_all %>% 
  group_by(real_mu) %>% 
  summarize(sample_size  = n(), rejects = sum(p.value < 0.05), proportion = rejects / sample_size)

ggplot(sim_summary, aes(x = real_mu, y = proportion)) + 
  geom_point() +
  geom_line() +
  labs(
    title = "Proportion of null rejected vs. Mean Value"
  )
```

From the plot we can see that as the real mean value of the data set furthers away from 0, the proportion of null rejected increases, suggesting that the two factors have a negative association.

Next, make a plot showing the average estimate of mu on the y axis and the true value of mu on the x axis. Make another plot that shows the average estimates of mu only in samples for which the null was rejected on the y axis and the true value of mu on the x axis.

```{r}
sim_all %>% 
  group_by(real_mu) %>% 
  summarize(mu_hat = mean(estimate)) %>% 
  ggplot(aes(x = real_mu, y = mu_hat)) +
  geom_point() +
  geom_line()
```

```{r}
sim_all %>% 
  group_by(real_mu) %>% 
  filter(p.value < 0.05) %>% 
  summarize(mu_hat = mean(estimate)) %>% 
  ggplot(aes(x = real_mu, y = mu_hat)) +
  geom_point() +
  geom_line()
```

By comparing the two generated plots above, we conclude that for true value of mean equal to 1, 2, and 3, the sample average for which the null is rejected doesn't approximately equal to the true value of mean, and the difference between the two means decreases as the true value of mean increases for these 3 cases. On the other hand, when the true value of mean equal to 0, 4, 5, and 6, the two means for comparison are approximately equal. 

This is because we tend to have a larger proportion of null rejected as the real mean value increases by the setting of our test. So the number of rejected cases increases with the increasing real mean value, making their mean approximates to the real mean, this explains the observation we see in the case of 4, 5, and 6. For the case of 0, since the null agrees with the real mean, the sum of rejected cases also follows a normal distribution with mean approximately to 0. For the case of 1, 2, and 3, the rejected cases are having higher mean compred to their real mean since cases with mean close to 0(i.e cases with smaller means) aren't rejected and this is more likely to happen with real mean close to 0, thus explaining the trend of decreasing magnitude of mean difference as we go from 1 to 3.