---
title: "p8105_hw5_sl5232"
author: "Shangsi Lin"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Load in data on homicides in large U.S. cities.

```{r}
homicides_df = read.csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"))
```

Observing the data set, which has `r nrow(homicides_df)` rows of observations and `r ncol(homicides_df)` columns of variables. We see that raw data is about homicides information across U.S. There are variables such as the id of the homicides, the date of report, victim's information, location that homicides belong to, and the disposition status.

Next, create a `city_state` variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides(for which the disposition is "Closed without arrest" or "Open/No arrest").

```{r}
homicides_df =
  homicides_df %>%
  mutate(city_state = str_c(city, state, sep = ",")) %>% 
  group_by(city_state) 

tibble_total = summarise(homicides_df, total_homicides = n())

tibble_unsolved =
  homicides_df %>% 
  filter(disposition != "Closed by arrest") %>% 
  summarise(unsolved_homicides = n())

full_join(tibble_total, tibble_unsolved)
```

Estimate the proportion of homicides that are unsolved for the city of Baltimore, MD. Save it as an R object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}

```


